\section{Further experiments: the direct macro levers}
\label{sec:experiments}

The bridge of Section~\ref{sec:bridge} covers reforms whose incidence is household-borne. This section works three experiments that instead pull the model's exogenous levers directly, chosen to exercise three different transmission channels: a pure demand-side expenditure shock, a pure price shock, and a cost-of-capital shock. All are run with \texttt{run\_reform} over 2025Q1--2027Q4 with the shock applied for twelve quarters; Table~\ref{tab:experiments} reports annual averages of the quarterly deviations, and the underlying quarterly paths are written to \texttt{figures/experiments\_quarterly.csv} by the script \texttt{figures/run\_experiments.py} that generated them.

\begin{table}[ht]
\centering
\caption{Three policy experiments through the direct levers, annual averages of quarterly deviations from the anchored baseline}
\label{tab:experiments}
\begin{tabular}{lrrrr}
\toprule
 & \multicolumn{1}{c}{$\Delta$GDP, \% } & \multicolumn{1}{c}{$\Delta$GDP} & \multicolumn{1}{c}{$\Delta$Consumption} & \multicolumn{1}{c}{$\Delta$Investment} \\
 & \multicolumn{1}{c}{of GDP} & \multicolumn{1}{c}{\pounds bn/qtr} & \multicolumn{1}{c}{\pounds bn/qtr} & \multicolumn{1}{c}{\pounds bn/qtr} \\
\midrule
\multicolumn{5}{l}{\emph{A. Government consumption $+$\pounds 5bn/yr} ($CGG$ $+$\pounds 1.25bn/qtr)}\\
\quad 2025 & $+0.18$ & $+1.250$ & $0.000$ & $0.000$ \\
\quad 2026 & $+0.19$ & $+1.250$ & $-0.000$ & $0.000$ \\
\quad 2027 & $+0.19$ & $+1.249$ & $-0.001$ & $0.000$ \\
\multicolumn{5}{l}{\emph{B. VAT-style price shock} (CPI level $+1$ per cent, $+1.4$ index points)}\\
\quad 2025 & $-0.15$ & $-1.014$ & $-1.014$ & $0.000$ \\
\quad 2026 & $-0.41$ & $-2.737$ & $-2.737$ & $0.000$ \\
\quad 2027 & $-0.46$ & $-3.070$ & $-3.070$ & $0.000$ \\
\multicolumn{5}{l}{\emph{C. Corporation tax $+$2pp} ($TCPRO$ $+0.02$, investment closure)}\\
\quad 2025 & $-0.005$ & $-0.034$ & $-0.000$ & $-0.034$ \\
\quad 2026 & $-0.04$ & $-0.295$ & $-0.004$ & $-0.290$ \\
\quad 2027 & $-0.13$ & $-0.901$ & $-0.014$ & $-0.880$ \\
\bottomrule
\end{tabular}

\medskip
\parbox{0.92\textwidth}{\footnotesize \emph{Notes:} Each experiment solves a structurally identical baseline and shocked pair (add-factors shared) and reports the delta, 2025Q1--2027Q4, shock applied for 12 quarters. Experiment C uses the investment closure with the reconstructed $\Delta \ln IBUSX$ equation~\eqref{eq:ibus} and the stabilised market-sector feedback (Section~\ref{sec:method}). Source: \texttt{figures/run\_experiments.py}; quarterly detail in \texttt{figures/experiments\_quarterly.csv}.}
\end{table}

\paragraph{A. Government consumption $+$\pounds 5bn a year.} The canonical demand shock: real $CGG$ rises \pounds 1.25bn per quarter. Under the demand closure the impact multiplier is one by construction---GDP rises by exactly the shock in 2025Q1---and the interesting content is what happens \emph{after} impact: the multiplier neither builds (no accelerator operates, because investment is a passthrough outside the investment closure) nor decays materially (imports are exogenous in this configuration, so the leakage that would normally erode a spending multiplier through equation~\eqref{eq:mgtfe} is inoperative), and consumption crowds out only trivially ($-$\pounds 1bn \emph{cumulative} by 2027Q4) through the small negative feedback of the price and income channels. The honest reading is that the emulator's $CGG$ multiplier of $\approx 1.0$ throughout is the direct mechanical effect plus approximately zero second-round dynamics, which brackets it between the OBR's own impact-multiplier assumptions for spending measures (below one once import leakage and offsets are applied \citep{obr2014costings}) and older Keynesian estimates above one: the emulator omits the import leakage (downward force) and the induced-income consumption loop (upward force) alike, and reports the shock arithmetic in between.

\paragraph{B. A VAT-style price shock.} Because the CPI is an exogenous conditioning path (Section~\ref{sec:model}), a one per cent rise in the consumer price level ($+1.4$ index points held for twelve quarters) is a legitimate lever, and it is the closest supported analogue to the price effect of an indirect-tax rise: the OBR's costing convention for VAT changes assumes passthrough into consumer prices, which then erode real incomes. The transmission here is the deflator chain $CPI \to PCE \to RHHDI$ into the consumption ECM~\eqref{eq:cons}: with nominal income initially unchanged, real income falls one per cent, and consumption follows---$-$0.15 per cent of GDP in 2025, deepening to $-$0.46 per cent ($-$\pounds 3.1bn per quarter) by 2027 as the error-correction term drags the consumption \emph{level} toward its lower long-run solution. The entire GDP effect is consumption ($\Delta CONS = \Delta GDP$ to the pound in Table~\ref{tab:experiments}), which is the configuration speaking: investment, trade, and the labour-demand response that would spread the shock are passthrough or exogenous here. For scale, HMRC's ready reckoner puts the \emph{direct revenue} of a 1pp VAT standard-rate rise at \pounds 8.8--9.6bn a year \citep{hmrc2025reckoner}; a full VAT scoring would put that costing through the bridge as an $HHDI$-equivalent real-income loss, and the experiment here isolates the complementary price-channel arithmetic on consumer demand.

\paragraph{C. Corporation tax $+$2pp, and why the bridge refuses it.} The bridge declines corporation-tax reforms by design: in the microsimulation, corporation tax has no household-resolution incidence---attributing it to households would smuggle in an incidence assumption (shareholders? workers? consumers?) that PolicyEngine's UK model deliberately does not make---so translating a corporation-tax costing into an $HHDI$ shock would be a category error, and the correct route is the model's own lever. Raising $TCPRO$ by two percentage points with the investment closure active works the user-cost channel $TCPRO \to TAF \to COC \to KSTAR \to KGAP \to IBUSX$: a higher tax rate raises the post-tax cost of capital, lowers desired capital, opens a capital-stock gap, and depresses business investment through the error-correction term of equation~\eqref{eq:ibus}. The response is small and slow---$-$\pounds 0.03bn per quarter in year one, building to $-$\pounds 0.9bn per quarter ($-$0.13 per cent of GDP) by 2027---exactly the profile the slow investment ECM ($\lambda = 0.042$) implies, and consistent in sign and magnitude class with the OBR's treatment of corporation-tax measures as chiefly a receipts effect with modest medium-term investment drag. For comparison, the \emph{direct} Exchequer yield of $+$2pp on the main rate is about \pounds 7.2bn in 2026--27 rising to \pounds 8.0bn in 2028--29 on HMRC's ready reckoner \citep{hmrc2025reckoner}; the emulator's contribution is the second-round path, not the static number. The response is hard-gated in CI for sign and boundedness (Table~\ref{tab:anchored}), and Section~\ref{sec:limitations} flags the stabilised closure it depends on as a stop-gap.

Across the three experiments a single lesson recurs: where a channel is live, the emulator reproduces the OBR architecture's sign, shape, and magnitude class; where a channel is passthrough, the emulator does not invent a response---it reports zeros and says why. That property---experiments degrade legibly rather than plausibly---is the design goal the honest scorecard of Section~\ref{sec:rawscore} exists to protect.
