\section{Limitations}
\label{sec:limitations}

The PolicyEngine Macro suite grades its members on a \emph{verification gradient}: how far each model's outputs can be audited against ground truth should temper the weight placed on its answers. The OBR emulator is a \emph{replication with a published anchor}---auditable against the EFO tables---which is a stronger epistemic position than a calibrated counterfactual, but the audit itself reveals clear limits. In the spirit of reporting them rather than rounding them away:

\begin{enumerate}
\item \textbf{The anchored fit is by construction, not skill.} The 0.18/0.29 per cent reproduction of the EFO (Table~\ref{tab:anchored}) demonstrates that the transmission chains are wired correctly; it says nothing about forecasting ability. All forecasting claims rest on the much weaker free-running and held-add-factor scorecards.

\item \textbf{The free-running model is weak, and says so.} Only 4 of 11 computed headline variables land within band; 10 of 21 are passthroughs held at the OBR value (Table~\ref{tab:rawscore}). The suite's documentation describes the free-running fit as ``deliberately report-only, and weak,'' and this paper endorses that description.

\item \textbf{Unpublished inputs impose hard floors.} The OBR does not publish its full databank: the $OSHH$ base constant (behind the 54.6 per cent company-profits error and the $\sim$15 per cent incomes errors), the $I7$/$PR$ index history (behind decaying RPI inflation), and the overseas rate-of-return normalisers (behind the current-account error) are unrecoverable from public sources. These errors are gated against regression, not chased to zero, because closing them would mean fitting to the answer.

\item \textbf{Dead and exogenised channels.} Exports, imports, CPI, the labour-demand block, and wages are exogenous in this configuration---held at the OBR path. Reforms whose first-round incidence runs through those channels (e.g.\ trade or supply-side labour measures) are outside the emulator's current scope, and employment ``accuracy'' is a trivial identity over two passthrough inputs.

\item \textbf{Two household-income equations do not fire.} The transpiler's left-hand-side parser recognises the $\mathrm{dlog}(X)$, $d(X)$, $X/X(-n)$ and level forms, but not a bare $\log(X)$ left-hand side. The October 2025 model file contains exactly two such equations---$\log(HHTFA)$ and $\log(NDIVHH)$---which are consequently indexed under a key that is not a databank column, so they never execute and their variables stay frozen at their historical paths. This is not cosmetic: $HHTFA$ enters $NMTRHH$ and $NDIVHH$ enters $PIRHH$, and both of those enter $HHDI$---the very quantity the microsimulation bridge shocks. In particular $\log(NDIVHH)$ is a function of lagged company profits $FYCPR$ and $CORP$, so household dividend income should respond to a corporate-profits change and here does not, which mutes the household-income channel of the corporation-tax experiment of Section~\ref{sec:experiments} specifically. The defect was found while investigating solver warning output; the warning is now raised once per solve and names the affected variables rather than being suppressed. The parser has since gained a $\log$ left-hand-side kind ($\log(X)=\mathit{rhs} \Rightarrow X=\exp(\mathit{rhs})$; merged upstream as obr-macroeconomic-model PR~\#16, after this paper's results were computed), but parser support does not by itself revive the equations, for a second and independent reason: their exogenous right-hand-side inputs, $MAJGDP$ and $CORP$, are absent from the databank entirely. No equation computes them and neither appears in the exogenous seed data, so the right-hand side would evaluate non-finite and the solver would skip the update. Parser support is therefore necessary but not sufficient: with the fix merged, the two lines remain passthroughs held at the OBR value, and the scorecard continues to report them as such. The channel's inertness is directly demonstrable---a five-percentage-point corporation-tax rise moves $FYCPR$ by $-\pounds1{,}780$m while $\Delta NDIVHH$ is exactly zero. Reviving the channel requires sourcing a $CORP$ series, which is a calibration decision rather than a code change: the fitted constant $-8.6056$ implies a scale the published OBR material does not document, and choosing one to make the level come out right would be fitting to the answer. Every figure in this paper is therefore computed with these two channels inert.

\item \textbf{Bridge assumptions are crude and declared.} The static costing lands entirely on nominal household disposable income, flat within each year; the economy's feedback onto disposable income is not recycled; incidence is demand-side only; and corporation-tax reforms are refused rather than mistranslated. Supply-side responses belong to the suite's OLG member.

\item \textbf{Vintage sensitivity and judgement contamination.} The ONS input snapshot is current-vintage data merged into an autumn-2025 baseline, so revision slack silently enters the add-factors; and the held-add-factor base window extends into quarters that are the OBR's own forecast, so ``held judgement'' partly means ``agree with the OBR.'' The forecast scorecard also inherits a jump-off flatter from EFO seeding.

\item \textbf{Stabilised, not structural, investment closure.} The corporation-tax investment closure freezes market-sector output feedback at a tracking-pass reference to suppress an explosive accelerator loop; the mandated sign and boundedness invariants hold, but the closure is a stop-gap pending a populated market-sector supply block, and it is computationally expensive on the hosted service.

\item \textbf{No official counterpart to check dynamics against.} The OBR publishes the model listing and a description \citep{obr2013model} but no official working paper, ready-reckoner of model multipliers, or reference simulation set for the current vintage; the emulator's shock responses can be checked for sign, magnitude class, and convention-consistency, but not line-by-line against an official impulse response.
\end{enumerate}
